\begin{thebibliography}{80}

    \bibitem{http://wikipedia:2019} wikipedia.
    ``\textbf{link: http://en.wikipedia.org/}'',
    \textit{}, truy cần lần cuối: 05/05/2019.
    
    
        \bibitem{Frey2016}	Frey, D., Makkes, M. X., Roman, P.-L., Taiani,  F.,  Voulgaris, S.: Bringing secure Bitcoin transactions to your smartphone. The 15th International Workshop on Adaptive and Reflective Middleware, (2016).
        
        \bibitem{Andreas2014} Antonopoulos, A. M.: Mastering Bitcoin. 2nd edn. O'Reilly Media, CA 95472 (2014).
        
        \bibitem{Bitcoinjs} Bitcoinjs: Open Source Organisation for Bitcoin JavaScript Libraries,https://github.com/bitcoinjs. Truy cần lần cuối vào 01/05/2019.
        
        \bibitem{Bitcoinj}	Bitcoinj: Library for working with the Bitcoin protocol,https://bitcoinj.github.io. Truy cần lần cuối vào 28/04/2019.
        
        \bibitem{Yanovich:2016} Yanovich, Y., Mischenko, P.,  Ostrovskiy,  A.:  Shared Send Untangling in Bitcoin, White paper, Bitfury Group Limited (2016).
        
        \bibitem{Patrick-Dai:2016} Dai, P., Mahi, N., Earls, J., Norta, A.: Smart-Contract Value-Transfer Protocols on a Distributed Mobile Application Platform, https://qtum.org/uploads/files/cf6d69348ca50dd985b60425ccf282f3.pdf, (2016).
        
        \bibitem{Sergi:2017} Sergi, D.-S., Cristina, P.-S., Guillermo, N.-A., Jordi, H.-J.: Analysis of the Bitcoin UTXO set, IACR Cryptology ePrint Archive, (2017).
        
        \bibitem{Mark-Erhardt:2016} Erhardt, M.: An Evaluation of Coin Selection
        Strategies, Master thesis, Karlsruhe Institute of Technology, URL: http://murch.one/wp-content/uploads/2016/11/erhardt2016coinselection.pdf, (2016).
        
        \bibitem{Zahnentferner:2018} Zahnentferner, J.: Chimeric ledgers: Translating and unifying utxo-based and account-based cryptocurrencies, Cryptology ePrint Archive, Report 2018/262, 2018. https://eprint.iacr.org/2018/262, (2018).
        
        \bibitem{Chepurnoy:2018} Chepurnoy, A., Kharin, V., Meshkov, D.: A Systematic Approach To Cryptocurrency Fees. IACR Cryptology ePrint Archive, (2018).
    \end{thebibliography}